Spin canonical divisors of log stacky curves

### 2015-06-19 stacky_write_up/spin_cring.tex
fix overtabbing
adding macro

\section{Effective Genus Zero Spin Divisors}
\label{sec:g_0_effective}
Let us consider $\delta \geq 2$.

@@

\begin{lem}
\label{sat_three_induction}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  and let $R_{\halfcan'} = R' = k[x]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $\halfcan = \subhalf i$. There are generators $y_3,y_4,y_5$ of $R_{\halfcan+\halfcan'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$. \todo{Include the order} 
Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively. \todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, letting $x_j$ range over all $x$ variables
\begin{align*}
	in_\prec(I) = in_\prec(I')k[x,y_3,\ldots, y_e,z_4,z_5] + \\
	\langle y_i y_j \mid 1 \leq i < j-3 \leq e \rangle +\\
	\langle y_i x_j \mid i > 3 \rangle +\\
	\langle z_i y_j \mid j > 3 \rangle  +\\
	\langle z_i x_j \mid 4 \leq i \leq 5\rangle + \\
	\langle z_iz_k \mid 4 \leq i \leq j \leq 5 \rangle 
\end{align*}

>>>>

\section{Effective Genus Zero Spin Divisors}
\label{sec:g_0_effective}
Suppose $\delta=\deg(\halfcan)>0$.  Then we can explicitly write out $D=K_\sx+\Delta=K_X+\sum \subhalf{i}$   Let us consider $\delta \geq 2$.

@@

\begin{lem}
\label{sat_three_induction}
Let $\sx \rightarrow \sx'$ be a birational map of tame, separably rooted  and let $R_{\halfcan'} = R' = k[x]/I'$ satisfy $sat(Eff(\halfcan')) = 3.$ Let $\halfcan = \subhalf i$. There are generators $y_3,y_4,y_5$ of $R_{\halfcan+\halfcan'}= R$ over $R'$ so that $y_i$ lies in degree $i$ and has a pole of order $1$. \todo{Include the order} 
Let $x_3,x_4,x_5$ be generators of $k[x]$ lying in degrees 3,4,5 respectively. \todo{Make sure to state some requirement on the ordering of the $x_i$, analogously to 8.4.1, but I don't see why this is important.} Then, l oetting $x_j$ range over all $x$ variables
\begin{align*}
	in_\prec(I) = in_\prec(I')k[x,y_3,\ldots, y_e,z_4,z_5] + \\
	\langle y_i y_j \mid 1 \leq i < j-3 \leq e \rangle +\\
	\langle y_i x_j \mid i > 3 \rangle +\\
	\langle z_i y_j \mid j > 3 \rangle  +\\
	\langle z_i x_j \mid 4 \leq i \leq 5\rangle + \\
	\langle z_iz_k \mid 4 \leq i \leq j \leq 5 \rangle 
\end{align*}
